Jeff Goldsmith

### 2018-06-01 index.Rmd
typo fix
fixing links; level up

### Assistant Professor of Biostatistics, Columbia University Mailman School of Public Health

@@

My full CV is availble [here](Downloads/CV_Goldsmith.pdf).

>>>>

### Associate Professor of Biostatistics, Columbia University Mailman School of Public Health

@@

My full CV is available [here](Downloads/CV_Goldsmith.pdf).
